---
title: "BIDS Apps"
author: "Nandi Vijayakumar"
date: "27 April 2018"
output: html_document
---

### Running MRIQC on HPC using Singularity
##### These scripts are saved under 'open_neuroscience_workshop/BIDS_apps/scripts/singularity/'
##### You will need three scripts: download_container.sh, job_mriqc.sh and batch_mriqc.sh.
##### You will also need a text file with the subject list with both ID and wave number: SID000,wave1

##### download_container.sh
```{r, engine = 'bash', eval = FALSE}
#!/bin/bash

#This script creates singulatiry containers for use on HPC. It needs to be run on a local machine (with Docker installed) and then transferred to HPC.

outputdir='/path/to/save/container/'

docker run --privileged -t --rm \
    -v /var/run/docker.sock:/var/run/docker.sock \
    -v ${outputdir}:/output \
    singularityware/docker2singularity \
    poldracklab/mriqc:latest \

#This can take a while to download. Once completed, copy the container to HPC.

```

##### batch_mriqc.sh (parallelize mriqc across subjects)
```{r, engine = 'bash', eval = FALSE}
#!/bin/bash
#
# This batch file calls on your subject list (which contains both ID and wave number: SID000,wave1). 
# And runs the job_mriqc.sh file for each subject. 
# It saves the ouput and error files in specified directories.
#
# Set your directories

container=/path/to/save/container/poldracklab_mriqc_latest-2017-10-19-8992ca9444b6.img
study_dir=/path/to/study/folder/ #set path to directory within which study folder lives
study="study_name" 

# Set subject list
SUBJLIST=`cat subject_list.txt`

# Loop through subjects and run job_mriqc
for SUBJ in $SUBJLIST; do

SUBID=`echo $SUBJ|awk '{print $1}' FS=","`
SESSID=`echo $SUBJ|awk '{print $2}' FS=","`
  
sbatch --export subid=${SUBID},sessid=${SESSID},study_dir=${study_dir},study=${study},container=${container} --job-name mriqc --partition=long -n16 --mem=75G --time=20:00:00 -o "${study_dir}"/"${study}"/scripts/singularity/output/"${SUBID}"_"${SESSID}"_mriqc_output.txt -e "${study_dir}"/"${study}"/scripts/singularity/output/"${SUBID}"_"${SESSID}"_mriqc_error.txt job_mriqc.sh

	
done
```

##### job_mriqc.sh (execute mriqc)
```{r, engine = 'bash', eval = FALSE}
#!/bin/bash

# This script runs mriqc on subjects located in the BIDS directory 
# and saves quality control outputs in the derivatives folder.

# Set bids directories
bids_dir="${study_dir}""${study}"/bids_data
derivatives="${bids_dir}"/derivatives/mriqc
working_dir="${derivatives}"/working
image="${study_dir}""${container}"

echo -e "\nMRIQC on ${subid}_${sessid}"
echo -e "\nContainer: $image"
echo -e "\nSubject directory: $bids_dir"

# Load packages
module load singularity

# Create working directory
mkdir -p $working_dir

# Run container using singularity
cd $bids_dir

singularity run --bind "${study_dir}":"${study_dir}" $image $bids_dir $derivatives participant --participant_label $subid --session-id $sessid -w $working_dir --n_procs 16 --mem_gb 64

echo -e "\n"
echo -e "\ndone"
echo -e "\n-----------------------"
```

##### Make sure job_mriqc.sh, batch_mriqc.sh and subject_list.txt are all in same folder. Then run batch script...
```{r, engine = 'bash', eval = FALSE}
sh batch_mriqc.sh
```
